---
title: "district_pattern_analysis"
author: "Yu He"
date: "2023-04-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libraries
```{r}
library(tidyverse)
library(haven)
library(caret)
library(nnet)
library(broom)
library(pROC)
library(rpart.plot)
```


## import the processed data
```{r}
# load the processed  state data
df_part1 = read_csv("./data/df_a_m.csv")
df_part2 = read_csv("./data/df_n_z.csv")

# merge two state dataset
df_f_project = bind_rows(df_part1, df_part2)

# load the district dataset
df_district = read_csv("./data/df_district.csv")
```


## data cleaning
```{r}
# the state data
df_fit_state <- 
  df_f_project %>% 
  filter(year == 2019) %>% 
  mutate(
  across(c("sex", "age", "grade", "race4", "qnothhpl"), as.factor),
  year = as.character(year)
  ) %>% 
  mutate_at(vars(starts_with("q")), as.factor) %>% 
  filter(q85 %in% c(1, 2, 3)) %>% 
  na.omit()

# the school distrcit data
df_fit_district <- 
  df_district %>% 
  filter(year == 2019) %>%
    mutate(
  across(c("sex", "age", "grade", "race4", "qnothhpl"), as.factor),
  year = as.character(year)
  ) %>% 
  mutate_at(vars(starts_with("q")), as.factor) %>%
  filter(q85 %in% c(1, 2, 3)) %>% 
  na.omit()

df_fit_state %>% 
  group_by(sitename) %>% 
  summarize(
    n_obs = n()
  )

df_fit_district %>% 
  group_by(sitename) %>% 
  summarize(
    n_obs = n()
  )

summary(df_fit_district)
summary(df_fit_state)
```



## check variables with 0 variance levels and re-create new variables for un-balanced variables
```{r}
# the modification for school district data
levels(df_fit_district$age)
levels(df_fit_district$q63)
levels(df_fit_district$q65)

# drop the level with 0
df_fit_district = df_fit_district %>% 
  # Remove levels from the factor column
  filter(!(age %in% c("1", "2"))) %>% 
  filter(q63 != 1) %>% 
  filter(q65 != 1) %>% 
  mutate(
  # Remove the unused levels from the factor column
     age = factor(age),
     q63 = factor(q63),
     q65 = factor(q65),
  # cover q50, q52, q53 to two level variables
  # 1 = 1, and 2 = the rest of observations
     q50 = ifelse(q50 == 1, 1, 2),
     q50 = factor(q50),
     q52 = ifelse(q52 == 1, 1, 2),
     q52 = factor(q52),
     q53 = ifelse(q53 == 1, 1, 2),
     q53 = factor(q53)
  ) 

summary(df_fit_district)


# the modification for state data
levels(df_fit_state$age)
levels(df_fit_state$q63)
levels(df_fit_state$q65)

# drop the level with 0
df_fit_state = df_fit_state %>% 
  # Remove levels from the factor column
  filter(age != 1) %>% 
  filter(q63 != 1) %>% 
  filter(q65 != 1) %>% 
  mutate(
  # Remove the unused levels from the factor column
     age = factor(age),
     q63 = factor(q63),
     q65 = factor(q65),
  # cover q50, q52, q53 to two level variables
  # 1 = 1, and 2 = the rest of observations
     q50 = ifelse(q50 == 1, 1, 2),
     q50 = factor(q50),
     q52 = ifelse(q52 == 1, 1, 2),
     q52 = factor(q52),
     q53 = ifelse(q53 == 1, 1, 2),
     q53 = factor(q53)
  ) 

summary(df_fit_state)
```




```{r}
df_ft = df_fit_district %>% 
  filter(sitename == "Broward County, FL (FT)") %>% 
  select(-sitename, -year)

df_ch = df_fit_district %>% 
  filter(sitename == "Chicago, IL (CH)") %>% 
  select(-sitename, -year)

df_ea = df_fit_district %>% 
  filter(sitename == "Eaton Consortium, MI (EA)") %>% 
  select(-sitename, -year)
```

```{r}
summary(df_ft)
summary(df_ft$q17)
summary(df_ch)
summary(df_ea)

```

# Variable Importance for every Local school districts
## Broward County, FL (FT)
```{r}
df_ft = df_fit_district %>% 
  filter(sitename == "Broward County, FL (FT)") %>% 
  select(-sitename, -year)



set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ft, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 50) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 50) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 50) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Chicago, IL (CH)
```{r}
df_ch = df_fit_district %>% 
  filter(sitename == "Chicago, IL (CH)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ch, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Eaton Consortium, MI (EA)
```{r}
df_ea = df_fit_district %>% 
  filter(sitename == "Eaton Consortium, MI (EA)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ea, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Fort Worth, TX (FW)
```{r}
df_fw = df_fit_district %>% 
  filter(sitename == "Fort Worth, TX (FW)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_fw, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Genesee Consortium, MI (GE)
```{r}
df_ge = df_fit_district %>% 
  filter(sitename == "Genesee Consortium, MI (GE)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ge, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Hillsborough County, FL (HL)
```{r}
df_hl = df_fit_district %>% 
  filter(sitename == "Hillsborough County, FL (HL)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_hl, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 50) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 50) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 50) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Los Angeles, CA (LO)
```{r}
df_lo = df_fit_district %>% 
  filter(sitename == "Los Angeles, CA (LO)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_lo, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 50) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 50) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 50) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Newark, NJ (NW)
```{r}
df_nw = df_fit_district %>% 
  filter(sitename == "Newark, NJ (NW)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_nw, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Orange County, FL (OL)
```{r}
df_ol = df_fit_district %>% 
  filter(sitename == "Orange County, FL (OL)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ol, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))


var_import = varImp(model_lasso)$importance
```


## Palm Beach County, FL (PB)
```{r}
df_ol = df_fit_district %>% 
  filter(sitename == "Palm Beach County, FL (PB)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ol, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Pasco County, FL (PS)
```{r}
df_ps = df_fit_district %>% 
  filter(sitename == "Pasco County, FL (PS)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ps, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Philadelphia, PA (PH)
```{r}
df_ph = df_fit_district %>% 
  filter(sitename == "Philadelphia, PA (PH)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_ph, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso, scale = FALSE)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso, scale = FALSE)$importance
```


## Portland, OR (PO)
```{r}
df_po = df_fit_district %>% 
  filter(sitename == "Portland, OR (PO)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_po, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))


var_import = varImp(model_lasso)$importance
```


## San Francisco, CA (SF)
```{r}
df_sf = df_fit_district %>% 
  filter(sitename == "San Francisco, CA (SF)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_sf, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))

var_import = varImp(model_lasso)$importance
```


## Shelby County, TN (ST)
```{r}
df_sf = df_fit_district %>% 
  filter(sitename == "Shelby County, TN (ST)") %>% 
  select(-sitename, -year)


set.seed(123)
#Create grid to search lambda
lambda <- 10^seq(-3,3, length = 100)

# Specify training control
train_control_lasso <- trainControl(method = "cv", number = 10)

model_lasso = train(q85 ~.,
                    df_sf, 
                    method = "glmnet", 
                    trControl = train_control_lasso, 
                    tuneGrid = expand.grid(alpha = 1, lambda = lambda))

summary(model_lasso)
model_lasso$bestTune
model_lasso$results

#Visualize accuracy versus values of C
plot(model_lasso)

#Obtain metrics of accuracy from training
confusionMatrix(model_lasso)

varImp(model_lasso)
plot(varImp(model_lasso))

var_importance = varImp(model_lasso)
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x1 > 10) %>% 
  select(x1) %>% 
  arrange(desc(x1))

var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x2 > 10) %>% 
  select(x2) %>% 
  arrange(desc(x2))
  
var_importance$importance %>% 
  janitor::clean_names() %>% 
  filter(x3 > 10) %>% 
  select(x3) %>% 
  arrange(desc(x3))


var_import = varImp(model_lasso)$importance
```




















